Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-05-05 article.tex
Add TMH predicting methods

For MHC-I, there are multiple computational tools developed 
to predict epitopes. 
According to \cite{lundegaard2011prediction}, in 2011,
from a set of multiple tools, 
NetMHCcons \cite{karosiene2012netmhccons} gave the best predictions.
A tool not included in this review is \verb;epitope-prediction;,
which uses a stabilized matrix method, as described in \cite{kim2009derivation}.
The reason this tool is mentioned, is because it is used 
in cite{bianchi2017}.

@@

\paragraph{Leftovers (to move or remove)}

\richel{This is nonsense: 'The polypeptides that can bind are also 
likelier to by hydrophobic,
as most TMHs have a hydrophobic binding pocket': \cite{lund2004definition}
uses the hydrophobicity of some peptides for classification, but this
does not mean the statement is true}
There are two sources of hydrophobic polypeptides, which are 
from membrane proteins and of soluble proteins.
Membrane proteins have at least one TMH to anchor them to
the membrane. TMHs are hydrophobic, as this is required to span the 
hydrophobic cellular lipid membrane. Additionally,
they often have a length of 23 amino acids to be able to span
the membrane.
Soluble proteins have (non-TMH) hydrophobic regions as well, 
to guides the protein to achieve its 3D configuration.

@@

\richel{Or someplace else. Reorganise!}

>>>>

For MHC-I, there are multiple computational tools developed 
to predict epitopes. 
According to \cite{lundegaard2011prediction}, in 2011,
from a set of multiple tools, 
NetMHCcons \cite{karosiene2012netmhccons} gave the best predictions.
A tool not included in this review is \verb;epitope-prediction;,
which uses a stabilized matrix method, as described in \cite{kim2009derivation}.
The reason this tool is mentioned, is because it is used 
in \cite{bianchi2017}.

@@

\paragraph{TMHs}

Transmembrane helices are conserved structures that span
a cell membrane with an alpha helix.
TMHs are hydrophobic, as this is required to span the 
hydrophobic cellular lipid membrane. Additionally,
they often have a length of 23 amino acids to be able to span
the membrane.
Polypeptide fragments derived from TMHs are among the most hydrophobic,
together with the internals of soluble proteins, where the
hydrophobicity parts guide the protein to achieve its 3D configuration.
TMHs are general structures: 25 percent of the human proteome is
anchored by at least one TMH. COVID-19 has 21 TMHs, 
making up for \richel{?} percent of its entire genome.

@@

There are multiple computational tools developed to detect which
parts of membrane proteins are TMH (as well as which side is inside
and outside).

In 2001, multiple tools to do so have been compared \cite{moller2001evaluation},
of which TMHMM \cite{krogh2001predicting} turned out to be the best.
A later method such as \cite{kall2004combined} \richel{I should check}.
Other later methods, such as ConPred II (\cite{arai2004conpred})
and MetaTM (\cite{klammer2009metatm}) show promises, but
appear to be unavailable \richel{Uh, both servers are down?!?!}.
